ext_risk_copula

### 2019-02-18 ext_risk_copula.Rmd
adding abrewer model

<!--
# Austin Brewer model :

@@

numsims<-10000
numsteps<-25
numlocs<-5
s<-0.2
K<-50
p0<-K
rc_abrewer<-1/(K*(1-exp(-s*K)))

@@

for(i in c(1:length(rlist))){
    r<- rlist[i]
    params<-c(r,K,s)
    ext_thrs<-p0/10

@@

# For global dispersal in D matrix 
res_abrewer_global<-c()
for(r in rlist){
    #cat("r=",r,"\n")
    params<-c(r,K,s)
    ext_thrs<-p0/10

@@

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Austin Brewer model with no dispersion : rc=0.02000091, scl=0.8); numlocs=5, numsteps=25, numsims=10000\label{fig_abrewer_risk_d0_scl_0.8}](./Results/austinbrewer_scl_0.8/abrewer_extrisk_d0.pdf){ width=40%, height=40% }
-->

>>>>

# Austin Brewer model :

@@

numsims<-10000
numsteps<-25
numlocs<-5
s<-0.2
K<-50

rc_abrewer<-1/(K*(1-exp(-s*K)))

@@

for(i in c(1:length(rlist))){
  r<- rlist[i]
  K<-50
  s<-0.2
  p0<-K
  params<-c(r,K,s)
  ext_thrs<-p0/10

@@

# For global dispersal in D matrix 
res_abrewer_global<-c()
for(r in rlist){
  #cat("r=",r,"\n")
  K<-50
  s<-0.2
  p0<-K
  params<-c(r,K,s)
  ext_thrs<-p0/10

@@

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Austin Brewer model with no dispersion : rc=0.02000091, scl=0.8); numlocs=5, numsteps=25, numsims=10000\label{fig_abrewer_risk_d0_scl_0.8}](./Results/austinbrewer_scl_0.8/abrewer_extrisk_d0.pdf){ width=40%, height=40% }
